Matching Bullets

### 2015-12-04 imaging-paper.Rnw
figures completed

lop <- lapply(reslist, function(res) {
ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), show.legend=FALSE, ymin=-6, ymax=5, data=res$lines, alpha=0.2) +
  geom_line(aes(x = y, y = l30, colour = bullet),   data = res$bullets) +
  scale_colour_brewer("", palette="Set1", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1.2), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match))
})

@@

\begin{figure}
<<barrel2, echo=FALSE, fig.width = 7.5, fig.height=7.5, out.width='\\linewidth', warning=FALSE>>=
thresholds <- seq(0.3, 1.5, by = 0.05)
list_of_matches <- lapply(19:24, function(i) {
  lof <- processBullets(paths = images[c(15,i)], x = 100)
  lof <- bulletSmooth(lof)

  subLOFx1 <- subset(lof, bullet==unique(lof$bullet)[1])
  subLOFx2 <- subset(lof, bullet==unique(lof$bullet)[2])

  # ccf assumes that both time series start at the same y
  subLOFx1$y <- subLOFx1$y - min(subLOFx1$y)
  subLOFx2$y <- subLOFx2$y - min(subLOFx2$y)
  ccf <- ccf(subLOFx1$l30, subLOFx2$l30, plot = FALSE, lag.max=150, na.action = na.omit)
  lag <- ccf$lag[which.max(ccf$acf)]

  subLOFx1$y <- subLOFx1$y -  lag * 1.5625 # amount of shifting should just be lag * y.inc
  lofX <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

#  browser()  
  CMS <- thresholds %>% lapply(function(threshold) {
    lines <- striation_identify(lofX, threshold = threshold)
    cms <- CMS(lines$match)
    data.frame(threshold=threshold, maxCMS = as.numeric(rev(names(cms)))[1])
  }) %>% bind_rows()

  threshold = CMS$threshold[which.max(CMS$maxCMS)]
  lines <- striation_identify(lofX, threshold = threshold)
  title <- gsub("app.*//","", images[i])
  title <- gsub(".x3p","", title)
  ggplot() +
    theme_bw() + 
    geom_rect(aes(xmin=miny, xmax=maxy), ymin=-6, ymax=5, fill="grey90", data=subset(lines, lineid!=0)) +
    geom_line(aes(x = y, y = l30, colour = bullet),  data = lofX) +
    geom_hline(yintercept = threshold) +
    geom_hline(yintercept = - threshold) +
    scale_colour_brewer(palette="Set1") +
    theme(legend.position = "none") + 
    ylim(c(-6,6)) + ylab("") + xlab("") +
    geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match & lineid !=0)) +
    geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match & lineid !=0)) +
    ggtitle(title) +
    theme(plot.margin=unit(c(1,0,0,0), unit="line"))
})

grid.arrange(list_of_matches[[1]], list_of_matches[[2]], list_of_matches[[3]], 
             list_of_matches[[4]], list_of_matches[[5]], list_of_matches[[6]],
             ncol = 2)
@
\caption{\label{fig:barrel2}All lands from the second bullet shot from barrel 2 are compared to the third land of the first bullet shot from barrel 2 (in red). The largest number of CMS is seven, observed with land four of the second bullet. }
\end{figure}

@@

print(ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax), ymin=-6, ymax=5, fill="grey90", data=res$lines) +
  geom_line(aes(x = y, y = l30, colour = bullet),  data = res$bullets) +
#  geom_hline(yintercept = res$threshold) +
#  geom_hline(yintercept = - res$threshold) +
  scale_colour_brewer(palette="Set1") +
  theme(legend.position = c(1,1), legend.justification=c(1,1)) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match)))

>>>>

lop <- lapply(reslist, function(res) {
ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), show.legend=FALSE, ymin=-6, ymax=5, data=res$lines, alpha=0.2) +
  geom_line(aes(x = y, y = l30, colour = bullet),   data = res$bullets) +
  scale_colour_brewer("", palette="Set1", na.value=alpha("grey50", alpha=0.5)) +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1.2), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match))
})

@@

\begin{figure}
<<barrel2, echo=FALSE, fig.width = 7, fig.height=12, out.width='\\linewidth', warning=FALSE>>=

list_of_matches <- lapply(25:30, function(i) {
  lof <- processBullets(paths = images[c(31,i)], x = 100)
  lof <- bulletSmooth(lof)

  bAlign = bulletAlign(lof)
  lofX <- bAlign$bullet

  b12 <- unique(lof$bullet)
  peaks1 <- get_peaks(subset(lofX, bullet==b12[1]), smoothfactor = 25)
  peaks2 <- get_peaks(subset(lofX, bullet == b12[2]), smoothfactor = 25)
  peaks1$lines$bullet = b12[1]
  peaks2$lines$bullet = b12[2]
  lines <- striation_identifyXXX(peaks1$lines, peaks2$lines)

  ggplot() +
    theme_bw() + 
    geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), show.legend=FALSE, ymin=-6, ymax=6, data=lines, alpha=0.2) +
    geom_line(aes(x = y, y = l30, colour = bullet),  data = lofX) +
#    geom_hline(yintercept = threshold) +
#    geom_hline(yintercept = - threshold) +
    scale_colour_brewer("",palette="Set1") +
    scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1.2), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
    ylim(c(-6,6)) + ylab("") + xlab("") +
    geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
    geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
    theme(plot.margin=unit(c(1,0,0,0), unit="line"))
})

grid.arrange(list_of_matches[[1]], list_of_matches[[2]], list_of_matches[[3]], 
             list_of_matches[[4]], list_of_matches[[5]], list_of_matches[[6]],
             ncol = 1)
@
\caption{\label{fig:barrel2}All lands from the first bullet shot from barrel 2 are compared to the first land of the second bullet shot from barrel 2 (in blue). The largest number of CMS is eleven, observed with land six of the second bullet. }
\end{figure}

@@

print(ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=5, data=res$lines, alpha=0.2, show.legend=FALSE) +
  geom_line(aes(x = y, y = l30, colour = bullet),  data = res$bullets) +
#  geom_hline(yintercept = res$threshold) +
#  geom_hline(yintercept = - res$threshold) +
  scale_colour_brewer("",palette="Set1") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1), legend.justification=c(1,1)) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match)))
